The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
better less ~ then -

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength varied in winter layers becoming stable at ~200 m and remained
consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
winter layers increased between ~10 - ~50 observations, remaining stable with
additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with fix
for open/rerun --> Like coarse landcover resolution (above), low numbers of
observations were not sufficient for capturing individuals in all contexts and
therefore layer similarity could not be calculated below approximately <!--TODO:
update these -->75 observations for forest, approximately 210 observations for
open and approximately 300 observations for forage (Figure \@ref(fig:nobs)c).
Once sufficient observations were obtained, layer similarity stabilized for all
three landcover classes at approximately 200 observations for forest and
approximately 300 observations for open and forage landcover types. Connective
redundancy increased dramatically between ~10 - ~50 observations before
stabilizing with all new observations included (Figure \@ref(fig:nobs)d). Given
the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.

@@

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 100 observations and remained weak throughout for summer layers. B) Mean layer relevance across individuals increased sharply for winter layers between ~10 - ~50 observations before stabilizing. Summer layers had consistent low layer relevance. C) Similarity of network layers across habitat classes and between seasons (e.g. open summer compared to open winter) was relatively consistent across number of observations for forest habitats. <!-- TODO: fix for open -->Note, open and forage habitats are not shown given no individuals interacted in the summer open and forage layers. D) Mean connective redundancy across individuals increased rapidly between ~10 - ~50 observations and then remained constant.

>>>>

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength varied in winter layers becoming stable at ~200 m and remained
consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
winter layers increased between ~10 m and ~50 m observations, remaining stable with
additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with fix
for open/rerun --> Like coarse landcover resolution (above), low numbers of
observations were not sufficient for capturing individuals in all contexts and
therefore layer similarity could not be calculated below approximately <!--TODO:
update these -->75 observations for forest, approximately 210 observations for
open and approximately 300 observations for forage (Figure \@ref(fig:nobs)c).
Once sufficient observations were obtained, layer similarity stabilized for all
three landcover classes at approximately 200 observations for forest and
approximately 300 observations for open and forage landcover types. Connective
redundancy increased dramatically between ~10 m and ~50 m observations before
stabilizing with all new observations included (Figure \@ref(fig:nobs)d). Given
the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.

@@

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 100 observations and remained weak throughout for summer layers. B) Mean layer relevance across individuals increased sharply for winter layers between ~10 m and ~50 m observations before stabilizing. Summer layers had consistent low layer relevance. C) Similarity of network layers across habitat classes and between seasons (e.g. open summer compared to open winter) was relatively consistent across number of observations for forest habitats. <!-- TODO: fix for open -->Note, open and forage habitats are not shown given no individuals interacted in the summer open and forage layers. D) Mean connective redundancy across individuals increased rapidly between ~10 m and ~50 m observations and then remained constant.
